Effect of character correlation

### 2018-03-27 Analysis/03-EffectCorrelationFigure.Rmd
typo

```{r, eval = TRUE, message = FALSE}
library(dispRity)
source("functions.R") ; load.functions(test = FALSE)
dyn.load("../Functions/char.diff.so")
load("../Data/NTS/matrix.nts.Rda")
source("../Data/load.data.R")
```

>>>>

```{r, eval = TRUE, message = FALSE}
library(dispRity)
source("functions.R") ; load.functions(test = FALSE)
load("../Data/NTS/matrix.nts.Rda")
source("../Data/load.data.R")
```
